Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-04-14 Multiresolution_framework/ltx/manuscript.tex
minor edit
added hay kin to bib

The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale. For cardinal B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
\begin{align}
 N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
 \end{align}
where 
 \begin{align}
\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
 \end{align}
and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients \citep{Chui1992}.

@@

Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood. For state-space models, the E-step corresponds to the smoothing problem, which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}. For the M-step, a lower bound on the likelihood function is constructed, where the steps needed
to compute the required quantities are very dependent on the particular application. This will be described in detail for our problem.

>>>>

The multi-resolution approximation using B-spline functions is completed by defining a two-scale relation pair, which relates the scaling functions and the wavelets at a given scale with the scaling function at the next higher scale. For B-spline scaling and wavelet functions of order $m$ the two-scale relation pair takes the form of
\begin{align}
 N_{m}\left(r\right)&=\sum_{n=0}^{m} \left[\mathbf p\right]_n N_{m}\left(2r-n\right) \label{eq:MRA-TwoScalepair1} \\
  \varphi_{m}\left(r\right) &= \sum_{n=0}^{3m-2}  \left[\mathbf q\right]_n N_{m}\left(2r-n\right)\label{eq:MRA-TwoScalepair2},
 \end{align}
where 
 \begin{align}
\left[\mathbf p\right]_n&=2^{-m+1} \binom{m}{n} \quad \text{ $0\le n\le m$} \label{eq:MRA-TwoScalepair1coefs}\\
\left[\mathbf q\right]_n&= \left(-1\right)^n{2^{-m+1}}\sum_{l=0}^{m} \binom{m}{l} N_{2m}\left(n-l+1\right), \,  \text{ $0\le n\le 3m-2$}\label{eq:MRA-TwoScalepair2coefs}
 \end{align}
and $\left[\cdot\right]_n$ denotes the $n^{th}$ element of the vector coefficients \citep{Chui1992}.

@@

Both the E and the M steps of the EM algorithm find increasingly tighter lower bounds on the likelihood of the parameters so that, at convergence, the maximum of the bound corresponds to the maximum of the likelihood. For state-space models, the E-step corresponds to the smoothing problem \citep{Haykin2001}, which can be solved using the Rauch Tung Streibel (RTS) smoother \cite{RAUCH1965}. For the M-step, a lower bound on the likelihood function is constructed, where the steps needed
to compute the required quantities are very dependent on the particular application. This will be described in detail for our problem.
